More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-09-27 2016-Weak-FH-Bisim/WeakBisim.tex
lemma 4: notations
reu rabea: symbols
changes
corollaire: weak FH-bisim

\section*{Status and TODO list}
Notes de reunion 24 Sept

@@

Intuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
\TODO{Id(s) is the identity function on variables of state s}
\begin{definition}[Non-observability of silent actions]
An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
\begin{enumerate}
\item
\[ \openrule
         {
           (j\mapsto\tau),\True,\Id(s)}
         {s \OTarrow {\tau} s}
         \in \mathcal{T}
\]
and 
\item for all $\alpha$, $j$, $s$, $\Post$ and $s'$ such that
\[ \openrule
         {
           (j\mapsto\tau),\Pred,\Post}
         {s \OTarrow {\alpha} s'}
         \in \mathcal{T} \] we have \[ \alpha=\tau\land s=s'\land \Post=\Id(s)
\]
\end{enumerate}
\end{definition}

@@

Two pNets are Weak FH-bisimilar if there exist a relation between their associated 
automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
the predicate associated to the relation between the initial states is \True.
 \end{definition}

@@

\begin{lemma} Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ be open automata and $<J,\mathcal{S}_1, s_0,
    \WT_1>$ be the
weak open automata derived from $A_1$.

\begin{itemize}
 \item  For any weak open transition $\symb{WOT} \in \WT$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

\end{mathpar}  
\TODO{!!! FAUX -- to REMOVE}
there exists  open transitions $\symb{OT} \in \mathcal{T}$:

\begin{mathpar}
     \openrule
         {
           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {\alpha} s'}

\end{mathpar}
 or $s=s'$ and $\alpha = \tau$
\end{itemize}

\begin{proof} 
We can rewrite $s \OTWeakarrow {} s'$ as follows $s \OTarrow {} s_1 \OTarrow {} \ldots \OTarrow {} s_n  \OTarrow {} s'$, we proceed by induction on the length of the inference of  ${s \OTWeakarrow {\alpha} s'}$ (introduced in Definition \ref{def:buildweakOT}). First, if  $\overline{\gamma}=\emptyset$ then using rule (1) we can directly conclude  $s=s'$ and $\alpha =\tau$. Otherwise, using  rule (2)  we have  s $\OTarrow {\alpha} s'$ and forall $j$, $\gamma_j=\vis{\beta_j}$. Second, using rule (3)  we have ${s \OTWeakarrow {\alpha} s'}$ implies ${s \OTWeakarrow {\tau} s_1} \OTWeakarrow {\alpha} s_2  \OTWeakarrow {\tau} s'$ and forall $j$, $\gamma_j = \gamma_{1j}\,\dotcup\,\gamma_{2j}\,\dotcup\,\gamma_{3j}$, and by induction hypothesis this means that there exist $s, s'$  such that $ s \OTarrow {\alpha} s'$ and $j$, $\gamma_{2j}=\vis{\beta_j}$.
\end{proof}   
\end{lemma}

\TODO{I am not sure that we have the same states between open auto 
and weak auto}

@@

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)  \Longleftrightarrow  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s', \quad
\overline{\gamma}=\biguplus_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^m \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
$

@@

\openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T} \implies 
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.   Induction step is to infer that formula holds for transitions of length $l + 1$. As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively).
We consider the case $n'=n+1$, $m'=m+1$ is similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction. Suppose we have:
\begin{mathpar}
\Bigg(\forall i \in [0\ldots n+1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg) 
\end{mathpar}

@@

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)  \implies  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
}
\end{mathpar}

@@

The right part of the disjunction, i.e.
\begin{mathpar}
\Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)
\end{mathpar}
is handled trivially by rule (\WTUn)

@@

\begin{itemize}
\item Case rule (\WTUn):
\begin{mathpar}
{ \openrule
         {
           \emptyset,\True,\Id(s)
				 } {s \OTWeakarrow {\tau} s} \in \WT
}
\end{mathpar}
In this case we can directly conclude by the right part of the disjunction.
\begin{mathpar}
{ \openrule
         {
           \emptyset,\True,\Id(s)
				 } {s \OTWeakarrow {\tau} s} \in \WT
} \implies \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)
\end{mathpar}

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have: 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots n_1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where \\
$ 
s=s^1_0 \wedge s^1_{n_1}\!=s_1,
\overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
$

\item Similarly, we have: 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \overline{\gamma_3},\Pred_3,\Post_3   }
         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
\bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots m_1].\openrule
    {
       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where\\
$
s_2=s^3_0 \wedge s^1_{m_1}=s',
\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}},
\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^3_i,\Post_3\!=\! \biguplus_{i=0}^{m_1} \Post_i^3\\
$

@@

\openrule
         {
           \overline{\beta^2},\Pred^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m_2].\openrule
         {
           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)         
\end{mathpar}
where\\
$
s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2,
\overline{\gamma_2}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta^3_i}}
\\
\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
\\
\Post_2= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
$
\end{enumerate}
~~\\

Therefore, we can deduce that:
\begin{mathpar}
\bigg( { \openrule
         {
           \overline{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\bigg)
 \Rightarrow
\Bigg(\forall i\in [0\ldots(n_1\!+\!n_2)].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in\mathcal{T} \wedge

@@

where\\
$
s_1\!=\!s^1_0 \wedge s^1_{n_1+n_2}\!=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}\!=\!s',
\overline{\gamma}=\biguplus_{i=0}^{n_1+n_2} \vis{\overline{\beta^1_i}} 
\dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_1+m_2} \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
\\
\Post= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
$

@@

Using this lemma, it is straightforward to see that....  
\begin{lemma}
Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
If $A_1$ and $A_2$ are weak FH-bisimilar then 
\begin{itemize}
 \item  For any weak open transition $\symb{WOT} \in \WT_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

@@

       	\begin{mathpar}  	
       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\openrule
       	{
       		\gamma_{jpxy}^{j\in J_{pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTWeakarrow {\alpha_{pxy}} u_{pxy}}\qquad (3)
       	%         \right)    	
       	\end{mathpar}
       	such that  $\forall y, J_{px}=J_{pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{px,pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred_{p,u} \land \Pred_{OT_{px}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. \gamma_{jpx}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\

>>>>

\section*{Status and TODO list}

Notes de reunion 24 Sept

@@

Intuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
\TODO{Id(s) is the identity function on variables of state s}
\begin{definition}[Non-observability of silent actions]
An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
\begin{enumerate}
\item
\[ \openrule
         {
           (j\mapsto\tau),\True,\Id(s)}
         {s \OTarrow {\tau} s}
         \in \mathcal{T}
\]
and 
\item for all $\alpha$, $j$, $s$, $\Post$ and $s'$ such that
\[ \openrule
         {
           (j\mapsto\tau),\Pred,\Post}
         {s \OTarrow {\alpha} s'}
         \in \mathcal{T} \] we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s)
\]
\end{enumerate}
\end{definition}

@@

Two pNets are weak FH-bisimilar if there exist a relation between their associated 
automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
the predicate associated to the relation between the initial states is \True.
 \end{definition}

@@

@@

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)  \Longleftrightarrow  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\overline{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
$

@@

\openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T} \implies 
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.   Induction step is to infer that formula holds for transitions of length $l + 1$. As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively).
We consider the case $n'=n+1$, and $m'=m+1$ are similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction. Suppose we have:
\begin{mathpar}
\Bigg(\forall i \in [0\ldots n+1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg) 
\end{mathpar}

@@

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)  \implies  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
}
\end{mathpar}

@@

The right part of the disjunction, i.e.
\begin{mathpar}
\Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
\end{mathpar}
is handled trivially by rule (\WTUn)

@@

\begin{itemize}
\item Case rule (\WTUn):
\begin{mathpar}
{\openrule
         {
           \emptyset,\True,\Id(s)
				 } {s \OTWeakarrow {\tau} s} \in \WT
}
\end{mathpar}
In this case we can directly conclude by the right part of the disjunction.
\begin{mathpar}
{ \openrule
         {
           \emptyset,\True,\Id(s)
				 } {s \OTWeakarrow {\tau} s} \in \WT
}\! \implies\! \Big(\alpha = \tau \wedge \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
\end{mathpar}

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have: 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots n_1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where \\
$ 
s=s^1_0 \wedge s^1_{n_1}\!=s_1,
\displaystyle{\overline{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\overline{\beta^1_i}}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
$

\item Similarly, a series of $m_1=n+m+1$  open transitions can be simplified: 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \overline{\gamma_3},\Pred_3,\Post_3   }
         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
\bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots m_1].\openrule
    {
       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where\\
$
s_2=s^3_0 \wedge s^1_{m_1}=s',
\displaystyle{\overline{\gamma_3}=\mybigdotcup_{i=0}^{m_1} \vis{\overline{\beta^3_i}}},
\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^3_i,\Post_3\!=\! \biguplus_{i=0}^{m_1} \Post_i^3\\
$

@@

\openrule
         {
           \overline{\beta^2},\Pred^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m_2].\openrule
         {
           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)         
\end{mathpar}
where\\
$
s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2,
\displaystyle{\overline{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}}  \mybigdotcup_{i=0}^{m_2} \vis{\overline{\beta^3_i}}}
\\
\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
\\
\Post_2= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
$
\end{enumerate}
~~\\
Therefore, we can deduce that:
\begin{mathpar}
\bigg( { \openrule
         {
           \overline{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\bigg)
 \Rightarrow
\Bigg(\forall i\in [0\ldots(n_1\!+\!n_2)].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in\mathcal{T} \wedge

@@

where\\
\[
\begin{array}{l}
s_1\!=\!s^1_0 \wedge s^1_{n_1+n_2}\!=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}\!=\!s'\\
\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\overline{\beta^1_i}}
\dotcup\vis{\overline{\beta^2}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\vis{\overline{\beta^3_i}}
}\\
\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}}
\\
\displaystyle{\Post= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}}
\end{array}
\]
\end{itemize}

@@

Using this lemma, it is straightforward to see that....

\begin{corollary} The definition of weak bisimulation given in  Definition \ref{def-Weak-bisim} is equivalent to the following weak FH-bisimulation: Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
For any  states
$s\in\mathcal{S}_1$ and
$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
   have:

 \begin{itemize}
 \item  For any open transition $\symb{WOT}$ in $\WT_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, \{j\in J_1|\gamma_j\neq\emptyset\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
$\Pred \land \Pred_{OT}\\
\displaystyle{\implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$

 \item  and symmetrically any open transition from $\symb{WOT}$ in $\WT_2$ can be 
      covered by a set of weak transitions from $s$ in $\WT_1$.
 \end{itemize}

\end{corollary}

\begin{lemma}
Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
If $A_1$ and $A_2$ are weak FH-bisimilar then 
\begin{itemize}
 \item  For any weak open transition $\symb{WOT} \in \WT_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

@@

       	\begin{mathpar}  	
       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\openrule
       	{
       		\gamma_{jpxy}^{j\in J_{pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTWeakarrow {\alpha_{pxy}} u_{pxy}}\qquad (3)
       	%         \right)    	
       	\end{mathpar}
       	such that  $\forall y, J_{px}=J_{pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{px,pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred_{p,u} \land \Pred_{OT_{px}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. \vis{\beta_{jpx}}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\
